Merits of hypermedia systems

### 2013-06-07 dagstuhl-2013/position.tex
Trim to 2 pages
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@590 43ef1190-90fd-4dd7-a769-d0121f02b80e
Final proofreading
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@591 43ef1190-90fd-4dd7-a769-d0121f02b80e

My primary research interest is the optimisation of SPARQL queries in
a federated regime, as we have noted that this is not practical
because the federation engine has insufficient information to
optimise, or the information is so large that it defeats the purpose
of optimisations to begin with. I plan to help remedy this problem by
computing very compact digests and expose them in the service
description. I have not yet published any articles on this topic, but
the research is in the immediate extension of
SPLENDID\cite{splendid}. My secondary research interest is replacing
the practice of benchmarking by using statistical design of
experiment.

@@

In \cite{kjernsmo_lapis_2012}, I examined some practical implications of
the HATEOAS constraint of the REST architectural style, see
\cite{Fielding_2000_Architectural-Styles}~Chapter~5., and in that
light argued why hypermedia RDF is a practical necessity.

@@

We continued to derive a powerful hypermedia type based on RDF within
a classification suggested by Mike Amundsen. Since this publication, I
have also noted that the embedded links factor can be achieved by
using \texttt{data} URIs, thus satisfying all but one of the factors
proposed by Mike Amundsen.

>>>>

My primary research interest is the optimisation of SPARQL queries in
a federated regime, as we have noted that this is not practical
because the federation engine has insufficient information to
optimise, or the information is so large that it defeats the purpose
of optimisations to begin with. I plan to help remedy this problem by
computing very compact digests and expose them in the service
description. I have not yet published any articles on this topic, but
the research is in the immediate extension of
SPLENDID\cite{splendid}. My secondary research interest is using statistical design of
experiment in software performance evaluation.

@@

In \cite{kjernsmo_lapis_2012}, I examined some practical implications of
the HATEOAS constraint of the REST architectural style, see
\cite{Fielding_2000_Architectural-Styles}~Chapter~5, and in that
light argued why hypermedia RDF is a practical necessity.

@@

We continued to derive a powerful hypermedia type based on RDF within
a classification suggested by Mike Amundsen. Since this publication, I
have also noted that the ``embedded links'' factor can be achieved by
using \texttt{data} URIs, thus satisfying all but one of the factors
proposed by Mike Amundsen.
